msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-14 paper.tex
Updates for paper read-through.

\begin{figure}
\includegraphics[width=\textwidth]{figures/recombination}
\caption{\label{fig-recombination-perf}(A) Approximate run time for \msprime\
simulations as a function of scaled recombination rate.
(B) Comparison of the ARG simulations vs minimal tree sequence representation.}
\end{figure}

@@

\begin{figure}
\caption{\label{fig-gc-perf}Comparison of the running time
for E-coli simulations using \msprime\ and SimBac for varying
sample sizes. The parameters used are [] based on [references].}
\end{figure}

@@

\subsection*{Discrete time Wright-Fisher}
The coalescent is a good approximation for ancient history, but
is bad for the recent past and in particular when we have large
sample
sizes~\citep{wakeley2012gene,bhaskar2014distortion,nelson2020accounting}.
Describe basic
approach [DOM, can you fill in please].
See ~\cite{nelson2020accounting} for more details.
We compare the performance of this simulation in Fig X
with ARGON~\citep{palamara2016argon}, a specialised DTWF simulator.

>>>>

\begin{figure}
\begin{center}
\begin{tabular}{cc}
\includegraphics[width=5cm]{msprime-scaling.png} &
\includegraphics[width=5cm]{figures/recombination} \\
\end{tabular}
\end{center}
% \includegraphics[width=\textwidth]{figures/recombination}
\caption{\label{fig-recombination-perf}(A) Approximate run time for \msprime\
simulations as a function of scaled recombination rate.
(B) Comparison of the ARG simulations vs minimal tree sequence representation.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{simbac.png}
\end{center}
\caption{\label{fig-gc-perf}Comparison of the running time
for E-coli simulations using \msprime\ and SimBac for varying
sample sizes. The parameters used are [] based on [references].}
\end{figure}

@@

\subsection*{Discrete time Wright-Fisher}
The coalescent is a good approximation for ancient history, but
is bad for the recent past and in particular when we have large
sample
sizes~\citep{wakeley2012gene,bhaskar2014distortion,nelson2020accounting}.
Describe basic
approach [DOM, can you fill in please].
See ~\cite{nelson2020accounting} for more details.
We compare the performance of this simulation in Fig.~\ref{fig-dtwf-perf}
with ARGON~\citep{palamara2016argon}, a specialised DTWF simulator.

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{msprime-argon-runtimes.png}
\end{center}
\caption{\label{fig-dtwf-perf} Comparison of \msprime's DTWF
simulations with ARGON. To ensure the comparison with ARGON is
as fair as possible we run it with a mutation rate of 0 and with
the minimum output options (so that it writes out only an empty VCF file)}
\end{figure}
